---
title: "p8105_hw5_sw3879"
author: "Siqing Wang"
date: "2023-11-11"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
library(purrr)
library(tidyr)
library(broom)
library(ggplot2)
library(forcats)
```

## Problem 1

Read in the raw data, create a new `city_state` variable
```{r}
homicide = read.csv("data/homicide-data.csv") |> 
  janitor::clean_names() |> 
  mutate(
    city_state = paste(city, state, sep = ", ")
  )
```

The raw dataset has `r nrow(homicide)` observations and `r ncol(homicide)` variables, which are `r colnames(homicide)`

Summarize within cities
```{r}
homicide_summary = homicide |> group_by(city_state) |> 
   summarize(total_homicides = n(),
             unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
   )

homicide_summary
```

Estimate the proportion of homicides that are unsolved in Baltimore MD
```{r}
baltimore_test = prop.test(
  homicide_summary |> filter(city_state == "Baltimore, MD") |> pull(unsolved_homicides),
  homicide_summary |> filter(city_state == "Baltimore, MD") |> pull(total_homicides)
) |>  broom::tidy()
```

The estimated proportion of unsolved homicides is `r baltimore_test |> pull(estimate)`. 
The confidence interval is [`r baltimore_test |> pull(conf.low)`, `r baltimore_test |> pull(conf.high)`].

Run prop test for each city
```{r}
nested_summary = homicide_summary %>%
  nest(total_homicides, unsolved_homicides)

all_cities_test = nested_summary %>%
  mutate(test_result = map(data, ~ prop.test(.x$unsolved_homicides, .x$total_homicides)))

all_cities_tidy = all_cities_test |> mutate(
    estimate = map_dbl(test_result, ~.x$estimate),
    conf_interval = map(test_result, glance),
    conf_interval_low = map_dbl(conf_interval, "conf.low"),
    conf_interval_high = map_dbl(conf_interval, "conf.high")
  ) %>%
  select(city_state, estimate, conf_interval_low, conf_interval_high) |> 
  filter(!estimate == 0)
```

Create a plot
```{r}
all_cities_tidy |> 
  mutate(city_state = fct_reorder(city_state,estimate))|>
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_errorbar(aes(ymin = conf_interval_low, ymax = conf_interval_high)) +
  geom_point() +
  theme(axis.text.x=element_text(angle = 45,hjust = 1)) +
  labs(title = "Estimates and Confidence Intervals for Unsolved Homicides by City",
       x = "City, State",
       y = "Estimated Proportion of Unsolved Homicides") +
  theme(axis.text.x = element_text(size = 7))
```



