---
title: "p8105_hw5_sw3879"
author: "Siqing Wang"
date: "2023-11-11"
output: html_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the raw data, create a new `city_state` variable
```{r}
homicide = read.csv("data/homicide-data.csv") |> 
  janitor::clean_names() |> 
  mutate(
    city_state = paste(city, state, sep = ", ")
  )
```

The raw dataset has `r nrow(homicide)` observations and `r ncol(homicide)` variables, which are `r colnames(homicide)`

Summarize within cities
```{r}
homicide_summary = homicide |> group_by(city_state) |> 
   summarize(total_homicides = n(),
             unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
   )

homicide_summary
```

Estimate the proportion of homicides that are unsolved in Baltimore MD
```{r}
baltimore_test = prop.test(
  homicide_summary |> filter(city_state == "Baltimore, MD") |> pull(unsolved_homicides),
  homicide_summary |> filter(city_state == "Baltimore, MD") |> pull(total_homicides)
) |>  broom::tidy()
```

The estimated proportion of unsolved homicides is `r baltimore_test |> pull(estimate)`. 
The confidence interval is [`r baltimore_test |> pull(conf.low)`, `r baltimore_test |> pull(conf.high)`].



